---
title: "Levels of the factor variable"
output:
  html_document: default
  pdf_document: default
date: "2024-01-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

- Y = perceived_gender + perceived_age + participantSex+  participantAge
OSM's can't handle interaction effects

Run this with BFGS using the new package version with SE turned off

```{r paquets, warning=FALSE, echo=FALSE,message=FALSE}
library(lme4)     #lmer
library(lmerTest)
library(ordinal)  #clm
library(readr)
library(dplyr)
library(stereord)
require(MASS)  #polr
require(Hmisc)
library(brant)  #test de paralelismo
library(VGAM)  #vglm
library(generalhoslem)
library(erer)  #marginals
library(MuMIn)  #R2 lmer
```

- arreglar los datos para que sean categoricos

```{r,  echo=FALSE,message=FALSE}
source("REading_data.R")
source("Functions_beauty.R")
path_int=   "../csv_storage/models/dependentAttributes"
path_attrac= "../csv_storage/models/attractiveness"
class(df$perceived_attractivenessfact)
class(df$imageGender)
class(df$perceived_age)
class(df$participantSex)
class(df$participantAge)
RUN_MODELS=FALSE
```

# ORIGINAL  images 
```{r ,  echo=FALSE}
df2 <- subset(df, df$beautification=="original")
```

```{r,  echo=FALSE}
file_name= paste(path_attrac,"M_OSM_withOUT_interactions_7L_ori.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =perceived_attractivenessfact ~ 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse levels

```{r,  echo=FALSE}
# original 6-7 colapse
df2$perceived_attractiveness_6L <- df2$perceived_attractivenessfact
df2$perceived_attractiveness_6L[ df2$perceived_attractivenessfact==7]=6
df2$perceived_attractiveness_6L <- droplevels(df2$perceived_attractiveness_6L)
# check
sort(unique(df2$perceived_attractiveness_6L))
table(df2$perceived_attractiveness_6L,df2$perceived_attractivenessfact)
```

```{r ,  echo=FALSE}
file_name= paste(path_attrac,"M_OSM_withOUT_interactions_6L_ori.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =perceived_attractiveness_6L ~ 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Attractiveness separated now. Next attribute 

## Intelligente

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_int7L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =intelligence_7L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse levels

```{r,  echo=FALSE}
# original 6-7 colapse
df2$intelligence_6L <- df2$intelligence_7L
df2$intelligence_6L[ df2$intelligence_6L==7]=6
df2$intelligence_6L <- droplevels(df2$intelligence_6L)
# check
sort(unique(df2$intelligence_6L))
table(df2$intelligence_6L,df2$intelligence_7L)
```

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_int6L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =intelligence_6L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 5 and 6 as well

```{r,  echo=FALSE}
# original 6-7 colapse
df2$intelligence_5L <- df2$intelligence_6L
df2$intelligence_5L[ df2$intelligence_5L==6]=5
df2$intelligence_5L <- droplevels(df2$intelligence_5L)
# check
sort(unique(df2$intelligence_5L))
table(df2$intelligence_5L,df2$intelligence_7L)
```

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_int5L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =intelligence_5L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Separable! Move onto the next attribute

## Happy

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_happy7L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =happy_7L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Seems separable. Move onto the next attribute

## sociability

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_sociability7L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =sociability_7L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 6 and 7

```{r,   echo=FALSE}
# original 6-7 colapse
df2$sociability_6L <- df2$sociability_7L
df2$sociability_6L[ df2$sociability_6L==7]=6
df2$sociability_6L <- droplevels(df2$sociability_6L)
# check
sort(unique(df2$sociability_6L))
table(df2$sociability_6L,df2$sociability_7L)
```

Rerun sociability on 6 levels

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_sociability6L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =sociability_6L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Separable. Move onto next attribute

## Unusual

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_unusual7L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =unusual_7L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 6 and 7
```{r,   echo=FALSE}
# original 6-7 colapse
df2$unusual_6L <- df2$unusual_7L
df2$unusual_6L[ df2$unusual_6L==7]=6
df2$unusual_6L <- droplevels(df2$unusual_6L)
# check
sort(unique(df2$unusual_6L))
table(df2$unusual_6L,df2$unusual_7L)
```

Re-run on 6 level
```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_unusual6L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =unusual_6L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 5 and 6
```{r,   echo=FALSE}
# original 6-7 colapse
df2$unusual_5L <- df2$unusual_6L
df2$unusual_5L[ df2$unusual_5L==6]=5
df2$unusual_5L <- droplevels(df2$unusual_5L)
# check
sort(unique(df2$unusual_5L))
table(df2$unusual_5L,df2$unusual_7L)
```

Re run on 5L
```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_unusual5L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =unusual_5L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 1 and 2

```{r,  echo=FALSE}
df2$unusual_4L <- df2$unusual_5L
df2$unusual_4L[ df2$unusual_4L==2]=1

for (i in 2:4) {df2$unusual_4L[ df2$unusual_4L==(i+1)]=i}
df2$unusual_4L <- droplevels(df2$unusual_4L)
# check
#sort(unique(df2$perceived_attractiveness_6L))
table(df2$unusual_4L,df2$unusual_7L)
```

Re run unusual on 4L
```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_unusual4L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =unusual_4L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 2 and 3
```{r,   echo=FALSE}
# original 6-7 colapse
df2$unusual_3L <- df2$unusual_4L
df2$unusual_3L[ df2$unusual_3L==3]=2
df2$unusual_3L[ df2$unusual_3L==4]=3
df2$unusual_3L <- droplevels(df2$unusual_3L)
# check
sort(unique(df2$unusual_5L))
table(df2$unusual_3L,df2$unusual_7L)
```

Re run unusual on 3 levels
```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_unusual3L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =unusual_3L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

## Trustworthy

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_trustworthy7L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =trustworthy_7L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Try collapsing 6 and 7

```{r,   echo=FALSE}
# original 6-7 colapse
df2$trustworthy_6L <- df2$trustworthy_7L
df2$trustworthy_6L[ df2$trustworthy_6L==7]=6
df2$trustworthy_6L <- droplevels(df2$trustworthy_6L)
# check
sort(unique(df2$trustworthy_6L))
table(df2$trustworthy_6L,df2$trustworthy_7L)
```

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_trustworthy6L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =trustworthy_6L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Much more separable now - move onto the next attribute

## feminine

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_feminine7L_ori_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =feminine_7L ~ perceived_attractiveness_6L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Seems separable already. Move onto the beautified images!

Save the original images dataframe!
```{r}
file_name= paste(path_int,"Original_Data_reescaled.RData", sep="")
save(df2,file=file_name)
write.csv(df2,paste0(path_int,"/","original_data_rescaled.csv"),row.names = FALSE)
```


# BEAUTIFIED  images 
```{r ,  echo=FALSE}
df2 <- subset(df, df$beautification=="beautified")
```

```{r ,  echo=FALSE}
file_name= paste(path_attrac,"M_OSM_withOUT_interactions_7L_beau.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =perceived_attractivenessfact ~
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```
Collapse 1 and 2

```{r,  echo=FALSE}
df2$perceived_attractiveness_6L <- df2$perceived_attractivenessfact
df2$perceived_attractiveness_6L[ df2$perceived_attractivenessfact==2]=1

for (i in 2:6) {df2$perceived_attractiveness_6L[ df2$perceived_attractiveness_6L==(i+1)]=i}
df2$perceived_attractiveness_6L <- droplevels(df2$perceived_attractiveness_6L)
# check
#sort(unique(df2$perceived_attractiveness_6L))
table(df2$perceived_attractiveness_6L,df2$perceived_attractivenessfact)
```

```{r ,  echo=FALSE}
file_name= paste(path_attrac,"M_OSM_withOUT_interactions_6L_beau.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =perceived_attractiveness_6L ~
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Merge 1 and 2 again
```{r,  echo=FALSE}
df2$perceived_attractiveness_5L <- df2$perceived_attractiveness_6L
df2$perceived_attractiveness_5L[ df2$perceived_attractiveness_5L==2]=1

for (i in 2:5) {df2$perceived_attractiveness_5L[ df2$perceived_attractiveness_5L==(i+1)]=i}
df2$perceived_attractiveness_5L <- droplevels(df2$perceived_attractiveness_5L)
# check
#sort(unique(df2$perceived_attractiveness_6L))
table(df2$perceived_attractiveness_5L,df2$perceived_attractivenessfact)
```

Re-run model now for 5 levels
```{r ,  echo=FALSE}
file_name= paste(path_attrac,"M_OSM_withOUT_interactions_5L_beau.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =perceived_attractiveness_5L ~
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

# Intelligence

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_int7L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =intelligence_7L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 6 and 7 - interesting because on the beautified set I was typically collapsing 1 and 2
```{r,   echo=FALSE}
# original 6-7 colapse
df2$intelligence_6L <- df2$intelligence_7L
df2$intelligence_6L[ df2$intelligence_6L==7]=6
df2$intelligence_6L <- droplevels(df2$intelligence_6L)
# check
sort(unique(df2$intelligence_6L))
table(df2$intelligence_6L,df2$intelligence_7L)
```
Re-run intelligence on 6 levels
```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_int6L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =intelligence_6L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

These values seem separable enough. Move onto the next dependent attribute

## happy

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_happy7L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =happy_7L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Seems separable enough

## sociability

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_sociability7L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =sociability_7L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 1 and 2
```{r,  echo=FALSE}
df2$sociability_6L <- df2$sociability_7L
df2$sociability_6L[ df2$sociability_6L==2]=1

for (i in 2:6) {df2$sociability_6L[ df2$sociability_6L==(i+1)]=i}
df2$sociability_6L <- droplevels(df2$sociability_6L)
# check
#sort(unique(df2$perceived_attractiveness_6L))
table(df2$sociability_6L,df2$sociability_7L)
```

Re-run sociability on 6 levels

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_sociability6L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =sociability_6L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

## Unusual

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_unusual7L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =unusual_7L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 1 and 2
```{r,  echo=FALSE}
df2$unusual_6L <- df2$unusual_7L
df2$unusual_6L[ df2$unusual_6L==2]=1

for (i in 2:6) {df2$unusual_6L[ df2$unusual_6L==(i+1)]=i}
df2$unusual_6L <- droplevels(df2$unusual_6L)
# check
#sort(unique(df2$perceived_attractiveness_6L))
table(df2$unusual_6L,df2$unusual_7L)
```

Re-run unusual on 6 levels
```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_unusual6L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =unusual_6L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 5 and 6 now
```{r,  echo=FALSE}
df2$unusual_5L <- df2$unusual_6L
df2$unusual_5L[ df2$unusual_5L==6]=5

df2$unusual_5L <- droplevels(df2$unusual_5L)
# check
#sort(unique(df2$perceived_attractiveness_6L))
table(df2$unusual_5L,df2$unusual_7L)
```
Re-run unusual on 5L
```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_unusual5L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =unusual_5L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 1 and 2
```{r,  echo=FALSE}
df2$unusual_4L <- df2$unusual_5L
df2$unusual_4L[ df2$unusual_4L==2]=1

for (i in 2:4) {df2$unusual_4L[ df2$unusual_4L==(i+1)]=i}
df2$unusual_4L <- droplevels(df2$unusual_4L)
# check
#sort(unique(df2$perceived_attractiveness_6L))
table(df2$unusual_4L,df2$unusual_7L)
```
Re-run unusual on 4L
```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_unusual4L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =unusual_4L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

1 and 2 are still very close - collapse again into 3?! levels

Collapse 1 and 2
```{r,  echo=FALSE}
df2$unusual_3L <- df2$unusual_4L
df2$unusual_3L[ df2$unusual_3L==2]=1

for (i in 2:3) {df2$unusual_3L[ df2$unusual_3L==(i+1)]=i}
df2$unusual_3L <- droplevels(df2$unusual_3L)
# check
#sort(unique(df2$perceived_attractiveness_6L))
table(df2$unusual_3L,df2$unusual_7L)
```

Re-run unusual on 3L
```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_unusual3L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =unusual_3L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

## trustworthy

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_trustworthy7L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =trustworthy_7L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 5 and 6

```{r,  echo=FALSE}
df2$trustworthy_6L <- df2$trustworthy_7L
df2$trustworthy_6L[ df2$trustworthy_6L==6]=5

# also collapse the 7's into 6's, but still a separate level from the new 5-6
df2$trustworthy_6L[ df2$trustworthy_6L==7]=6
df2$trustworthy_6L <- droplevels(df2$trustworthy_6L)

# check
#sort(unique(df2$perceived_attractiveness_6L))
table(df2$trustworthy_6L,df2$trustworthy_7L)
```

Re-run the trustworthy 6L

```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_trustworthy6L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =trustworthy_6L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

## feminine


```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_feminine7L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =feminine_7L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Collapse 1 and 2
```{r,  echo=FALSE}
df2$feminine_6L <- df2$feminine_7L
df2$feminine_6L[ df2$feminine_6L==2]=1

for (i in 2:6) {df2$feminine_6L[ df2$feminine_6L==(i+1)]=i}
df2$feminine_6L <- droplevels(df2$feminine_6L)
# check
#sort(unique(df2$perceived_attractiveness_6L))
table(df2$feminine_6L,df2$feminine_7L)
```
Re-run feminine 6L
```{r ,  echo=FALSE}
file_name= paste(path_int,"M_OSM_feminine6L_beau_Attrac6.RData", sep="")
if(RUN_MODELS){
  M_OSM <- OSM(formula =feminine_6L ~ perceived_attractiveness_5L + 
                              perceived_gender + perceived_age + 
                              participantSex +  participantAge , 
                              data = df2 ,phi1.iszero = TRUE, repar = TRUE, Approx.start.values = FALSE,  
                              method =  "BFGS", HES = FALSE, SE=FALSE,
                              control = list(maxit = 10000, reltol = 1e-6))
  save(M_OSM, file=file_name)
}
load(file_name)
M_OSM$phi
```

Seems separable now

Save the beautified dataframe!
```{r}
file_name= paste(path_int,"Beauty_Data_reescaled.RData", sep="")
save(df2,file=file_name)
write.csv(df2,paste0(path_int,"/","beautified_data_rescaled.csv"),row.names = FALSE)
```


