---
title: "Tests performed on the medians in the main paper"
output: html_document
date: "2024-05-28"
---

Tests are all performed on datafiles that were generated using python. 
All the CSV's can be found in the corresponding CSV folder in this project.

The current file uses the OSM models that are computed and stored in the folder named "models" with these scripts
The code to compute the OSM's can be found in the file: "computingNewSpacing_OSM.Rmd". Running this model requires access to the "stereord" R package which is still under development as of the day of the creation of this file. 

This file contains all the analysis done on the medians. The analysis with the complete datafile can be found in mainPaperTests_fullData.Rmd


Load all the necessary packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(ggcorrplot)
library(dplyr)
library(psych)
library(factoextra)
library(nparMD)
library(car)
library(ggpubr)
```

Load all the necessary datafiles
(Paths based on working directory being set to source file location)
```{r data,  echo=FALSE}

medians_df <- read_csv("../csv_storage/allAttributesMedians_df.csv")
pairedMedians_df <- read_csv("../csv_storage/pairedMedians_df.csv")

medians_df$dataset        <- as.factor(medians_df$dataset)
medians_df$beautification <- as.factor(medians_df$beautification)
medians_df$imageGender    <- as.factor(medians_df$imageGender)
medians_df$condition      <- as.factor(medians_df$condition)

pairedMedians_df$dataset        <- as.factor(pairedMedians_df$dataset)
pairedMedians_df$beautification <- as.factor(pairedMedians_df$beautification)
pairedMedians_df$imageGender    <- as.factor(pairedMedians_df$imageGender)
pairedMedians_df$condition      <- as.factor(pairedMedians_df$condition)

df_cfd <- subset(medians_df, medians_df$dataset=="cfd")
df_cfd<- droplevels(df_cfd)

df_cfd_original <- subset(df_cfd, df_cfd$beautification=="original")
df_cfd_original<- droplevels(df_cfd_original)

df_cfd_beautified <- subset(df_cfd, df_cfd$beautification=="beautified")
df_cfd_beautified<- droplevels(df_cfd_beautified)

df_original <- subset(medians_df, medians_df$beautification=="original")
df_original<- droplevels(df_original)

df_beautified <- subset(medians_df, medians_df$beautification=="beautified")
df_beautified<- droplevels(df_beautified)

df_faces <- subset(medians_df, medians_df$dataset=="faces")
df_faces$condition <- droplevels(df_faces$condition)
df_faces$condition  <- factor(df_faces$condition, levels=c("young","middle", "old"))

df_faces_original <- subset(df_faces, df_faces$beautification=="original")
df_faces_original<- droplevels(df_faces_original)

df_faces_beautified <- subset(df_faces, df_faces$beautification=="beautified")
df_faces_beautified<- droplevels(df_faces_beautified)
```


Wilcoxon paired rank test on the attractiveness - filters impact perceptions of attractiveness

```{r}
wilcox.test(pairedMedians_df$perceived_attractiveness_beautified,pairedMedians_df$perceived_attractiveness_original,paired = TRUE,alternative="greater")
```


Kendalls tau between attractiveness and delta attractiveness
```{r}
deltaAttractiveness_df <- read_csv("../csv_storage/delta_attractiveness_df.csv")
deltaAttractiveness_df$dataset        <- as.factor(deltaAttractiveness_df$dataset)
deltaAttractiveness_df$imageGender    <- as.factor(deltaAttractiveness_df$imageGender)
deltaAttractiveness_df$condition      <- as.factor(deltaAttractiveness_df$condition)

cor.test(deltaAttractiveness_df$perceived_attractiveness_original,deltaAttractiveness_df$increaseInAttrac, method="kendal")
```

KW on attractiveness on the age, gender and ethnicity
```{r}
# original images

###age
kruskal.test(perceived_attractiveness ~ condition, data=df_faces_original)

###gender
kruskal.test(perceived_attractiveness ~ imageGender, data=df_original)

###ethnicity
kruskal.test(perceived_attractiveness ~ condition, data=df_cfd_original)

# beautified images

###age
kruskal.test(perceived_attractiveness ~ condition, data=df_faces_beautified)

###gender
kruskal.test(perceived_attractiveness ~ imageGender, data=df_beautified)

###ethnicity
kruskal.test(perceived_attractiveness ~ condition, data=df_cfd_beautified)

```

pairwise wilcoxon test on attractiveness for age, gender and ethnicity
```{r}
# original images

###age
pairwise.wilcox.test(df_faces_original$perceived_attractiveness,df_faces_original$condition)

###gender
pairwise.wilcox.test(df_original$perceived_attractiveness,df_original$imageGender)

###ethnicity
pairwise.wilcox.test(df_cfd_original$perceived_attractiveness,df_cfd_original$condition)

# beautified images

###age
pairwise.wilcox.test(df_faces_beautified$perceived_attractiveness,df_faces_beautified$condition)

###gender
pairwise.wilcox.test(df_beautified$perceived_attractiveness,df_beautified$imageGender)

###ethnicity
pairwise.wilcox.test(df_cfd_beautified$perceived_attractiveness,df_cfd_beautified$condition)
```

Wilcoxon paired rank tests on the dependent attributes - filters impact perceptions of dependent attributes
```{r}
wilcox.test(pairedMedians_df$intelligence_beautified,pairedMedians_df$intelligence_original,paired = TRUE,alternative="greater")
wilcox.test(pairedMedians_df$trustworthy_beautified,pairedMedians_df$trustworthy_original,paired = TRUE,alternative="greater")
wilcox.test(pairedMedians_df$happy_beautified,pairedMedians_df$happy_original,paired = TRUE,alternative="greater")
wilcox.test(pairedMedians_df$sociability_beautified,pairedMedians_df$sociability_original,paired = TRUE,alternative="greater")
```

Simple linear models on all the dependent attributes
```{r}
# original set

M <- lm(intelligence ~ perceived_attractiveness, data = df_original)
print(summary(M))

M <- lm(trustworthy ~ perceived_attractiveness, data = df_original)
print(summary(M))

M <- lm(sociability ~ perceived_attractiveness, data = df_original)
print(summary(M))

M <- lm(happy ~ perceived_attractiveness, data = df_original)
print(summary(M))

# beautified images

M <- lm(intelligence ~ perceived_attractiveness, data = df_beautified)
print(summary(M))

M <- lm(trustworthy ~ perceived_attractiveness, data = df_beautified)
print(summary(M))

M <- lm(sociability ~ perceived_attractiveness, data = df_beautified)
print(summary(M))

M <- lm(happy ~ perceived_attractiveness, data = df_beautified)
print(summary(M))
```

Confidence intervals for the B1's of the simple linear models
```{r}
M <- lm(happy ~ perceived_attractiveness, data = df_original)
print("original")
print(confint(M, level=0.95))
print("")
print("\n------------\n")
print("")
M <- lm(happy ~ perceived_attractiveness, data = df_beautified)
print("beautified")
print(confint(M, level=0.95))
```
```{r}
ggplot(medians_df, aes(x = perceived_attractiveness, y = intelligence, color=beautification)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, level = 0.95) +
  theme_minimal() + 
  theme(legend.position = "none",plot.title = element_text(hjust = 0.5)) + 
  scale_color_manual(values = c("original" = "#e7a254", "beautified" = "#c1b4f9")) +
  labs(title = "Attractivenes vs. Intelligence - PRI and POST Data",
       x = "Attractiveness",
       y = "Intelligence")
```
