---
title: "Original"
output: html_document
date: "2023-11-07"
---

```{r setup,  echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 
- classical halo effect

```{r paquets, warning=FALSE, echo=FALSE,message=FALSE}
library(lme4)    # lmer
library(lmerTest)
library(ordinal) # clm
library(readr)
library(dplyr)
#library(stereord)
require(MASS) # polr
require(Hmisc)
library(brant) # test de paralelismo
library(VGAM) # vglm
library(generalhoslem)
library(erer) # marginals
library(MuMIn) # R2 lmer
```

- Running all the models with the categorical and re-scaled linear data to see how well all of them actually fit on the data we have

```{r loadData, echo=FALSE}

df_beautified <- read_csv("../csv_storage/beautified_data_rescaled_numeric.csv")
df_original <- read_csv("../csv_storage/original_data_rescaled_numeric.csv")

# convert all the categorical data to factors
df_beautified$dataset          <- as.factor(df_beautified$dataset)
df_beautified$beautification   <- as.factor(df_beautified$beautification)
df_beautified$imageGender      <- as.factor(df_beautified$imageGender)
df_beautified$perceived_gender <- as.factor(df_beautified$perceived_gender)
df_beautified$condition        <- as.factor(df_beautified$condition)
df_beautified$participantSex   <- as.factor(df_beautified$participantSex)

df_beautified$intelligence_origRating <- factor(df_beautified$intelligence_origRating,ordered = TRUE)
df_beautified$happy_origRating         <- factor(df_beautified$happy_origRating,ordered = TRUE)
df_beautified$sociability_origRating   <- factor(df_beautified$sociability_origRating,ordered = TRUE)
df_beautified$trustworthy_origRating   <- factor(df_beautified$trustworthy_origRating,ordered = TRUE)
df_beautified$perceived_attractiveness_origRating      <- factor(df_beautified$perceived_attractiveness_origRating,ordered = TRUE)

df_beautified$intelligence_collapsed <- factor(df_beautified$intelligence_collapsed,ordered = TRUE)
df_beautified$happy_collapsed         <- factor(df_beautified$happy_collapsed,ordered = TRUE)
df_beautified$sociability_collapsed   <- factor(df_beautified$sociability_collapsed,ordered = TRUE)
df_beautified$trustworthy_collapsed   <- factor(df_beautified$trustworthy_collapsed,ordered = TRUE)
df_beautified$perceived_attractiveness_collapsed      <- factor(df_beautified$perceived_attractiveness_collapsed,ordered = TRUE)


df_original$dataset          <- as.factor(df_original$dataset)
df_original$beautification   <- as.factor(df_original$beautification)
df_original$imageGender      <- as.factor(df_original$imageGender)
df_original$perceived_gender <- as.factor(df_original$perceived_gender)
df_original$condition        <- as.factor(df_original$condition)
df_original$participantSex   <- as.factor(df_original$participantSex)

df_original$intelligence_origRating <- factor(df_original$intelligence_origRating,ordered = TRUE)
df_original$happy_origRating         <- factor(df_original$happy_origRating,ordered = TRUE)
df_original$sociability_origRating   <- factor(df_original$sociability_origRating,ordered = TRUE)
df_original$trustworthy_origRating   <- factor(df_original$trustworthy_origRating,ordered = TRUE)
df_original$perceived_attractiveness_origRating      <- factor(df_original$perceived_attractiveness_origRating,ordered = TRUE)

df_original$intelligence_collapsed <- factor(df_original$intelligence_collapsed,ordered = TRUE)
df_original$happy_collapsed         <- factor(df_original$happy_collapsed,ordered = TRUE)
df_original$sociability_collapsed   <- factor(df_original$sociability_collapsed,ordered = TRUE)
df_original$trustworthy_collapsed   <- factor(df_original$trustworthy_collapsed,ordered = TRUE)
df_original$perceived_attractiveness_collapsed      <- factor(df_original$perceived_attractiveness_collapsed,ordered = TRUE)

# the numeric columns need to stay numeric
```

```{r setVar}
savePathBase <- "../csv_storage/models/modelFitTests"

dependent_attr <- "sociability" #perceived_attractiveness, feminine, happy, intelligence, trustworthy, unusual, sociability  or the other dependent attributes
beautification <- "beautified"

savePath <- paste(savePathBase,dependent_attr,beautification,sep="/")

if(beautification == "original"){
  df <- df_original
}else{
  df <- df_beautified
}
# the models for the other dependent attributes are different - include attractiveness as a variable

# need to move to my windows partition for an R installation that can handle the clm and clmm
RUN_MODELS_ORDINAL <- FALSE
RUN_MODELS_LINEAR <- TRUE
```

 Run the different models and store their results

 - Ordinal model
 - Non collapsed scales (all 7L, all factors), 
 - Raters as fixed effects

```{r  clm_fe_origL_ord, echo=FALSE}
cellAttributeType <- "_origRating"
fileName <- paste0(savePath,"/","clm_fe_origL_ord.Rdata")

modelString = "perceived_gender + perceived_age +  
               participantSex + participantAge  +
               perceived_gender:participantSex + perceived_age:participantAge"

if(dependent_attr == "perceived_attractiveness"){
 modelString <- paste0("perceived_attractiveness",cellAttributeType," ~ ",modelString)
}else{
  modelString <- paste0("perceived_attractiveness",cellAttributeType,"+",modelString) # add perceived attractiveness as one of the model parameters first
  modelString <- paste0(dependent_attr,cellAttributeType," ~ ",modelString)
}

if(RUN_MODELS_ORDINAL){
  clm_fe_origL_ord <- clm(as.formula(modelString),data = df)
  save(clm_fe_origL_ord,file=fileName)
}
load(fileName)
clm_fe_origL_ord
```
 
 - Ordinal model
 - Non collapsed scales (all 7L, all factors), 
 - Raters as random effects

```{r  clmm_re_origL_ord, echo=FALSE}
cellAttributeType <- "_origRating"
fileName <- paste0(savePath,"/","clmm_re_origL_ord.Rdata")

modelString = "perceived_gender + perceived_age +  
               participantSex + participantAge  +
               (1|prolificParticipantID) +
               perceived_gender:participantSex + perceived_age:participantAge"

if(dependent_attr == "perceived_attractiveness"){
 modelString <- paste0("perceived_attractiveness",cellAttributeType," ~ ",modelString)
}else{
  modelString <- paste0("perceived_attractiveness",cellAttributeType,"+",modelString) # add perceived attractiveness as one of the model parameters first
  modelString <- paste0(dependent_attr,cellAttributeType," ~ ",modelString)
}

if(RUN_MODELS_ORDINAL){
  clmm_re_origL_ord <- clmm(as.formula(modelString),data = df)
  save(clmm_re_origL_ord,file=fileName)
}
load(fileName)
clmm_re_origL_ord
```

 - Ordinal model
 - Collapsed scales for all attributes, treated as ordinal variables, 
 - Raters as fixed effects

```{r  clm_fe_osmL_ord, echo=FALSE}
cellAttributeType <- "_collapsed"
fileName <- paste0(savePath,"/","clm_fe_osmL_ord.Rdata")

modelString = "perceived_gender + perceived_age +  
               participantSex + participantAge  +
               perceived_gender:participantSex + perceived_age:participantAge"

if(dependent_attr == "perceived_attractiveness"){
 modelString <- paste0("perceived_attractiveness",cellAttributeType," ~ ",modelString)
}else{
  modelString <- paste0("perceived_attractiveness",cellAttributeType,"+",modelString) # add perceived attractiveness as one of the model parameters first
  modelString <- paste0(dependent_attr,cellAttributeType," ~ ",modelString)
}

if(RUN_MODELS_ORDINAL){
  clm_fe_osmL_ord <- clm(as.formula(modelString),data = df)
  save(clm_fe_osmL_ord,file=fileName)
}
load(fileName)
clm_fe_osmL_ord
```

 - Ordinal model
 - Collapsed scales for all attributes, treated as ordinal variables, 
 - Raters as random effects

```{r  clmm_re_osmL_ord, echo=FALSE}
cellAttributeType <- "_collapsed"
fileName <- paste0(savePath,"/","clmm_re_osmL_ord.Rdata")

modelString = "perceived_gender + perceived_age +  
               participantSex + participantAge  +
               (1|prolificParticipantID) +
               perceived_gender:participantSex + perceived_age:participantAge"

if(dependent_attr == "perceived_attractiveness"){
 modelString <- paste0("perceived_attractiveness",cellAttributeType," ~ ",modelString)
}else{
  modelString <- paste0("perceived_attractiveness",cellAttributeType,"+",modelString) # add perceived attractiveness as one of the model parameters first
  modelString <- paste0(dependent_attr,cellAttributeType," ~ ",modelString)
}

if(RUN_MODELS_ORDINAL){
  clmm_re_osmL_ord <- clmm(as.formula(modelString),data = df)
  save(clmm_re_osmL_ord,file=fileName)
}
load(fileName)
clmm_re_osmL_ord
```

# End of ordinal model computation

# Now start building the linear models

## First start with re-interpreting the factors as numeric columns to be able to pass them into the linear model functions

```{r convertToNumeric, echo=FALSE}
df$intelligence_origRating  <- as.numeric(df$intelligence_origRating)
df$happy_origRating         <- as.numeric(df$happy_origRating)
df$sociability_origRating   <- as.numeric(df$sociability_origRating)
df$unusual_origRating       <- as.numeric(df$unusual_origRating)
df$trustworthy_origRating   <- as.numeric(df$trustworthy_origRating)
df$feminine_origRating      <- as.numeric(df$feminine_origRating)
df$perceived_attractiveness_origRating <- as.numeric(df$perceived_attractiveness_origRating)

df$intelligence_collapsed  <- as.numeric(df$intelligence_collapsed)
df$happy_collapsed         <- as.numeric(df$happy_collapsed)
df$sociability_collapsed   <- as.numeric(df$sociability_collapsed)
df$unusual_collapsed       <- as.numeric(df$unusual_collapsed)
df$trustworthy_collapsed   <- as.numeric(df$trustworthy_collapsed)
df$feminine_collapsed      <- as.numeric(df$feminine_collapsed)
df$perceived_attractiveness_collapsed <- as.numeric(df$perceived_attractiveness_collapsed)
```

 - Linear model
 - Non collapsed scales (all 7L, all numeric), 
 - Raters as fixed effects

```{r  lm_fe_origL_lin, echo=FALSE}
cellAttributeType <- "_origRating"
fileName <- paste0(savePath,"/","lm_fe_origL_lin.Rdata")

modelString = "perceived_gender + perceived_age +  
               participantSex + participantAge  +
               perceived_gender:participantSex + perceived_age:participantAge"

if(dependent_attr == "perceived_attractiveness"){
 modelString <- paste0("perceived_attractiveness",cellAttributeType," ~ ",modelString)
}else{
  modelString <- paste0("perceived_attractiveness",cellAttributeType,"+",modelString) # add perceived attractiveness as one of the model parameters first
  modelString <- paste0(dependent_attr,cellAttributeType," ~ ",modelString)
}

if(RUN_MODELS_LINEAR){
  lm_fe_origL_lin <- lm(as.formula(modelString),data = df)
  save(lm_fe_origL_lin,file=fileName)
}
load(fileName)
lm_fe_origL_lin
```

 - Linear model
 - Non collapsed scales (all 7L, all numeric), 
 - Raters as random effects

```{r  lmer_re_origL_lin, echo=FALSE}
cellAttributeType <- "_origRating"
fileName <- paste0(savePath,"/","lmer_re_origL_lin.Rdata")

modelString = "perceived_gender + perceived_age +  
               participantSex + participantAge  +
               (1|prolificParticipantID) +
               perceived_gender:participantSex + perceived_age:participantAge"

if(dependent_attr == "perceived_attractiveness"){
 modelString <- paste0("perceived_attractiveness",cellAttributeType," ~ ",modelString)
}else{
  modelString <- paste0("perceived_attractiveness",cellAttributeType,"+",modelString) # add perceived attractiveness as one of the model parameters first
  modelString <- paste0(dependent_attr,cellAttributeType," ~ ",modelString)
}

if(RUN_MODELS_LINEAR){
  lmer_re_origL_lin <- lmer(as.formula(modelString),data = df)
  save(lmer_re_origL_lin,file=fileName)
}
load(fileName)
lmer_re_origL_lin
```

 - Linear model
 - Collapsed scales, but equidistant (all not 7L, all numeric), 
 - Raters as fixed effects

```{r  lm_fe_osmColL_lin, echo=FALSE}
cellAttributeType <- "_collapsed"
fileName <- paste0(savePath,"/","lm_fe_osmColL_lin.Rdata")

modelString = "perceived_gender + perceived_age +  
               participantSex + participantAge  +
               perceived_gender:participantSex + perceived_age:participantAge"

if(dependent_attr == "perceived_attractiveness"){
 modelString <- paste0("perceived_attractiveness",cellAttributeType," ~ ",modelString)
}else{
  modelString <- paste0("perceived_attractiveness",cellAttributeType,"+",modelString) # add perceived attractiveness as one of the model parameters first
  modelString <- paste0(dependent_attr,cellAttributeType," ~ ",modelString)
}

if(RUN_MODELS_LINEAR){
  lm_fe_osmColL_lin <- lm(as.formula(modelString),data = df)
  save(lm_fe_osmColL_lin,file=fileName)
}
load(fileName)
lm_fe_osmColL_lin
```

 - Linear model
 - Collapsed scales, but equidistant (all not 7L, all numeric), 
 - Raters as random effects

```{r  lmer_re_osmColL_lin, echo=FALSE}
cellAttributeType <- "_collapsed"
fileName <- paste0(savePath,"/","lmer_re_osmColL_lin.Rdata")

modelString = "perceived_gender + perceived_age +  
               participantSex + participantAge  +
               (1|prolificParticipantID) +
               perceived_gender:participantSex + perceived_age:participantAge"

if(dependent_attr == "perceived_attractiveness"){
 modelString <- paste0("perceived_attractiveness",cellAttributeType," ~ ",modelString)
}else{
  modelString <- paste0("perceived_attractiveness",cellAttributeType,"+",modelString) # add perceived attractiveness as one of the model parameters first
  modelString <- paste0(dependent_attr,cellAttributeType," ~ ",modelString)
}

if(RUN_MODELS_LINEAR){
  lmer_re_osmColL_lin <- lmer(as.formula(modelString),data = df)
  save(lmer_re_osmColL_lin,file=fileName)
}
load(fileName)
lmer_re_osmColL_lin
```

 - Linear model
 - Collapsed scales, distances changed too (all numeric), 
 - Raters as fixed effects

```{r  lm_fe_osmFinalL_lin, echo=FALSE}
cellAttributeType <- "_rescaledNumeric"
fileName <- paste0(savePath,"/","lm_fe_osmFinalL_lin.Rdata")

modelString = "perceived_gender + perceived_age +  
               participantSex + participantAge  +
               perceived_gender:participantSex + perceived_age:participantAge"

if(dependent_attr == "perceived_attractiveness"){
 modelString <- paste0("perceived_attractiveness",cellAttributeType," ~ ",modelString)
}else{
  modelString <- paste0("perceived_attractiveness",cellAttributeType,"+",modelString) # add perceived attractiveness as one of the model parameters first
  modelString <- paste0(dependent_attr,cellAttributeType," ~ ",modelString)
}

if(RUN_MODELS_LINEAR){
  lm_fe_osmFinalL_lin <- lm(as.formula(modelString),data = df)
  save(lm_fe_osmFinalL_lin,file=fileName)
}
load(fileName)
lm_fe_osmFinalL_lin
```

 - Linear model
 - Collapsed scales, distances changed too (all numeric),  
 - Raters as random effects

```{r  lmer_re_osmFinalL_lin, echo=FALSE}
cellAttributeType <- "_rescaledNumeric"
fileName <- paste0(savePath,"/","lmer_re_osmFinalL_lin.Rdata")

modelString = "perceived_gender + perceived_age +  
               participantSex + participantAge  +
               (1|prolificParticipantID) +
               perceived_gender:participantSex + perceived_age:participantAge"

if(dependent_attr == "perceived_attractiveness"){
 modelString <- paste0("perceived_attractiveness",cellAttributeType," ~ ",modelString)
}else{
  modelString <- paste0("perceived_attractiveness",cellAttributeType,"+",modelString) # add perceived attractiveness as one of the model parameters first
  modelString <- paste0(dependent_attr,cellAttributeType," ~ ",modelString)
}

if(RUN_MODELS_LINEAR){
  lmer_re_osmFinalL_lin <- lmer(as.formula(modelString),data = df)
  save(lmer_re_osmFinalL_lin,file=fileName)
}
load(fileName)
lmer_re_osmFinalL_lin
```
Try running the linear model with contrasts set to both the gender attributes so that I can see the interaction terms clearly
```{r, echo=TRUE}
cellAttributeType <- "_rescaledNumeric"
fileName <- paste0(savePath,"/","lmer_re_osmFinalL_lin.Rdata")

modelString = "perceived_gender + perceived_age +  
               participantSex + participantAge  +
               (1|prolificParticipantID) +
               perceived_gender:participantSex + perceived_age:participantAge"

if(dependent_attr == "perceived_attractiveness"){
 modelString <- paste0("perceived_attractiveness",cellAttributeType," ~ ",modelString)
}else{
  modelString <- paste0("perceived_attractiveness",cellAttributeType,"+",modelString) # add perceived attractiveness as one of the model parameters first
  modelString <- paste0(dependent_attr,cellAttributeType," ~ ",modelString)
}

if(RUN_MODELS_LINEAR){
  lmer_re_osmFinalL_lin <- lmer(as.formula(modelString),data = df,contrasts = list(perceived_gender = contr.treatment, participantSex = contr.treatment))
  #save(lmer_re_osmFinalL_lin,file=fileName)
}
#load(fileName)
summary(lmer_re_osmFinalL_lin)
a```
```


##  Models comparation AIC and BIC

- AIC
```{r, echo=FALSE}

a <- c(
0,#AIC(clm_fe_origL_ord),
0,#AIC(clmm_re_origL_ord),
0,#AIC(clm_fe_osmL_ord),
0,#AIC(clmm_re_osmL_ord),
AIC(lm_fe_origL_lin),
AIC(lmer_re_origL_lin),
AIC(lm_fe_osmColL_lin),
AIC(lmer_re_osmColL_lin),
AIC(lm_fe_osmFinalL_lin),
AIC(lmer_re_osmFinalL_lin)
)

  
Vnames <- c(
"clm_fe_origL_ord",
"clmm_re_origL_ord",
"clm_fe_osmL_ord",
"clmm_re_osmL_ord",
"lm_fe_origL_lin",
"lmer_re_origL_lin",
"lm_fe_osmColL_lin",
"lmer_re_osmColL_lin",
"lm_fe_osmFinalL_lin",
"lmer_re_osmFinalL_lin"
)

names(a) <- Vnames
index <- order(a)

a[index]

```

- BIC : bayesian information critrion

```{r, echo=FALSE}

a <- c(
BIC(clm_fe_origL_ord),
BIC(clmm_re_origL_ord),
BIC(clm_fe_osmL_ord),
BIC(clmm_re_osmL_ord),
BIC(lm_fe_origL_lin),
BIC(lmer_re_origL_lin),
BIC(lm_fe_osmColL_lin),
BIC(lmer_re_osmColL_lin),
BIC(lm_fe_osmFinalL_lin),
BIC(lmer_re_osmFinalL_lin)
)

names(a) <- Vnames
index <- order(a)

a[index]

```

# previous conclusions

- better with random effects on the rater than without
- better categorical factor than continuous
- better 6-categorical factor than 7categorical factor 

